---
title: "Week 3 Assignment"
author: "JJD"
date: "2/14/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## International Food Security

The dataset from the annual International Food Security Assessment report includes regional and sub-regional level data for the demand for grains (food and non-food), grain production, and the implied additional grain supply requirement (IASR) for the current year and 10-years out. 

The IASR quantifies the total grain demand in each region and sub-region that is not projected to be met through domestic production.

```{r data, include=FALSE, echo = TRUE}
library(plotly)
library(xlsx)
setwd("/Users/jenniferdimaano/Desktop/CourseraR/Developing Data Products/")
grainData<-read.xlsx("GrainDemandProduction.xlsx", sheetIndex = 1, header = TRUE)
```


## Grain Data
```{r data read, include=TRUE, comment=NA}
head(grainData)
```

## Asia Total
```{r graph load, include=TRUE, echo=FALSE}
asiaDataTotal <- grainData[which(grainData$Sub.region=="Asia, Total"), ]
plot_ly(asiaDataTotal, x = asiaDataTotal$Element, y = asiaDataTotal$Millions.of.metric.tons, type='bar', color = as.factor(asiaDataTotal$Year))
```
Total grain demand in Asia will increase ~22% in 2031.

## Sub Regions of Asia
```{r graph, include=FALSE, echo=FALSE}
asiaDataTotal1 <- grainData[which(grainData$Sub.region=="Commonwealth of Independent States"), ]
fig1<-plot_ly(asiaDataTotal1, x = asiaDataTotal1$Element, y = asiaDataTotal1$Millions.of.metric.tons, type='bar', color = as.factor(asiaDataTotal1$Year)) %>% layout(xaxis = list(title = 'Commonwealth of Independent States'))

asiaDataTotal2 <- grainData[which(grainData$Sub.region=="Central and Southern Asia"), ]
fig2<-plot_ly(asiaDataTotal2, x = asiaDataTotal2$Element, y = asiaDataTotal2$Millions.of.metric.tons, type='bar', color = as.factor(asiaDataTotal2$Year)) %>% layout(xaxis = list(title = 'Central and Southern Asia'))
```
```{r figure1, include=TRUE, echo=FALSE}
fig3 <- subplot(fig1, fig2, titleX = TRUE) %>% 
   layout(title = 'Asia')
fig3
```
## Sub Regions of Asia Continued
```{r, include=FALSE, echo=FALSE}
asiaDataTotal3 <- grainData[which(grainData$Sub.region=="Other Asia"), ]
fig4<-plot_ly(asiaDataTotal3, x = asiaDataTotal3$Element, y = asiaDataTotal3$Millions.of.metric.tons, type='bar', color = as.factor(asiaDataTotal3$Year)) %>% layout(xaxis = list(title = 'Other Asia'))

asiaDataTotal4 <- grainData[which(grainData$Sub.region=="Southeast Asia"), ]
fig5<-plot_ly(asiaDataTotal4, x = asiaDataTotal4$Element, y = asiaDataTotal4$Millions.of.metric.tons, type='bar', color = as.factor(asiaDataTotal$Year)) %>% layout(xaxis = list(title = 'Southeast Asia'))
```
```{r figure2, include=TRUE, echo=FALSE}
fig6 <- subplot(fig4, fig5, titleX = TRUE)
fig6
```